\documentclass[11pt,letterpaper]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx} % Times New Roman font
\usepackage[margin=0.5in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}

% Remove page numbers
\pagenumbering{gobble}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

% Section formatting - underlined headers
\titleformat{\section}
    {\normalfont\large\bfseries}
    {}
    {0em}
    {}
    [\titlerule]

\titlespacing*{\section}{0pt}{12pt}{6pt}

% Reduce spacing in lists
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=*}

% Custom commands
\newcommand{\projectheader}[2]{\textbf{#1} \textit{(#2):}}

\begin{document}

%====================
% HEADER
%====================
\begin{center}
    {\LARGE \textbf{Youssef Ragab}}\\[4pt]
    2301 E St NW, Washington, DC, 20037\textbar\ 857-308-8669\\[2pt]
    \href{mailto:yragab99@gmail.com}{yragab99@gmail.com} \textbar\ 
    \href{https://linkedin.com/in/yragab}{linkedin.com/in/yragab} \textbar\
    \href{https://github.com/yragab}{github.com/yragab}
\end{center}

%====================
% PROFESSIONAL SUMMARY
%====================
\section*{PROFESSIONAL SUMMARY}
Results-driven AI/Machine Learning Engineer with 4+ years of experience designing, developing, and deploying production-grade AI systems in high-stakes fintech environments. Proven expertise in fine-tuning Large Language Models (LLMs) and building scalable MLOps pipelines on cloud platforms (AWS/Azure). Passionate about leveraging Generative AI to drive intelligent automation, enhance data analytics, and build robust enterprise solutions. At Verituity, architected and deployed ML models that now secure over \$7B in transactions.

%====================
% TECHNICAL SKILLS
%====================
\section*{TECHNICAL SKILLS}
\begin{itemize}
    \item \textbf{Languages:} Python, SQL, Go, R, Java, Shell Scripting
    \item \textbf{AI/ML Frameworks:} PyTorch, TensorFlow, Scikit-learn, Pandas, NumPy, NLTK
    \item \textbf{GenAI \& NLP:} Large Language Models (LLMs), Fine-Tuning, OpenAI API, Anomaly Detection, Ensemble Methods
    \item \textbf{Cloud \& MLOps:} AWS, Azure, Docker, Kubernetes, CI/CD, Kafka, Dagster, Azure ML Studio
    \item \textbf{APIs \& Databases:} REST, gRPC, FastAPI, PostgreSQL (SQL), NoSQL
    \item \textbf{Developer Tools:} Git, Power BI, Apache Spark, Hadoop
\end{itemize}

%====================
% PROFESSIONAL EXPERIENCE
%====================
\section*{PROFESSIONAL EXPERIENCE}

\noindent\textbf{Verituity} -- Machine Learning Engineer \hfill 2022 -- Present\\
\textit{McLean, VA}
\begin{itemize}
    \item Architected and deployed over 25 production-grade machine learning models for identity verification and fraud detection, directly contributing to the platform's capacity to securely process over \$7B in transactions.
    \item Engineered and maintained scalable APIs (REST, gRPC) to serve model predictions, integrating AI capabilities into core enterprise backend systems and data pipelines.
    \item Developed a Generative AI solution by fine-tuning an LLM for context-based anomaly detection in financial data, achieving 100\% machine-readable JSON output for automated decision support.
    \item Implemented and managed a cloud-native MLOps workflow using Docker, Kafka, and Dagster on AWS/Azure, automating model training and deployment pipelines and reducing retraining time by over 80\%.
    \item Collaborated with cross-functional product and engineering teams to translate business requirements into robust, AI-driven features, from ideation and prototyping to production deployment.
\end{itemize}

%====================
% PROJECTS
%====================
\section*{PROJECTS}

\projectheader{Production-Grade AI Fraud Detection System}{Python, FastAPI, gRPC, Docker, PostgreSQL, AWS}
\begin{itemize}
    \item Designed and deployed a suite of ML models for real-time fraud and identity risk prediction, achieving over 90\% accuracy. Built scalable API endpoints for seamless integration into the enterprise platform.
    \item Engineered an automated model execution system using Kafka and Dagster, enabling end-to-end ownership by the data science team and reducing dependency on platform engineers.
\end{itemize}

\projectheader{Generative AI for Anomaly Detection}{Python, LLM Fine-Tuning, OpenAI API, PostgreSQL}
\begin{itemize}
    \item Fine-tuned a Large Language Model (LLM) to identify anomalies in platform financial data, creating a powerful tool for intelligent automation and decision support.
    \item Engineered a Python package to enforce structured JSON responses, enabling reliable integration with automated workflow and decision-support systems.
\end{itemize}

\projectheader{MLOps Automation Pipeline}{Python, Scikit-learn, Azure ML Studio, Docker, CI/CD}
\begin{itemize}
    \item Built an end-to-end automated pipeline for feature engineering, model training, and experimentation. Leveraged Docker and CI/CD practices to ensure reproducible and efficient model lifecycle management.
    \item Decreased time-to-retrain and deploy a new model by over 80\% through robust automation.
\end{itemize}

%====================
% EDUCATION
%====================
\section*{EDUCATION}

\noindent\textbf{Master of Science in Business Analytics} \hfill May 2022\\
The George Washington University, Washington, DC\\
Concentration: Business Analytics\vspace{8pt}\\

\noindent\textbf{Bachelor of Business Administration} \hfill May 2021\\
The George Washington University, Washington, DC\\
Concentration: Business Analytics, Marketing; Minor: Statistics

\end{document}
